---
title: "Day 4 Part 2 Exploring Data"
author: "Kiran Favre"
format: html
editor: visual
---

## Remember: if you want to know more about a function or anything, use '?\_\_\_\_' in the console

```{r}
#| warning: false
#| echo: false

# ^ code chunk headers 
#if you don't want to include these packages in the rendered doc, you can adjust by using code chunk options

library(tidyverse)
library(palmerpenguins)
library(GGally)  #had to install
library(skimr)  #had to install

```

## Exploratory data visualization

Check out your data a bit (not included in rendered because we chose to not using a code chunk operator):

```{r}
#| include: false


#tell me the column names 
names(penguins)


# What are the dimensions
dim(penguins)

# Can you show me the first 6 lines?
head(penguins)

#Last 6?
tail(penguins)
```

```{r}

#| echo: false
#only shows code, not output

2+10

```

```{r}
skim(penguins)  #using skimr package
```

```{r}
#| include: false

#u can explicitly name package used by naming package :: function
GGally::ggpairs(penguins)
```

## Jitter plot

Flipper length by species

```{r}
#| fig.cap = "My awesome figure caption"

ggplot(data = penguins, aes(x = species, y = flipper_length_mm)) + 
  geom_jitter(width = 0.2,
              alpha = 0.5,
              aes(color = species)) +
  geom_boxplot(fill = NA) +
              theme_classic() +
              scale_color_manual(values = c("darkorchid4", "cyan4", "goldenrod")) +
              labs( x = "Penguin Species ",
                    y = "Flipper length (mm)",
                    )
```

-   width changes distance of dots from eachother

-   alpha changes opacity

## Histograms

```{r}
ggplot(data = penguins, aes(x = bill_length_mm)) +
  geom_histogram(aes(fill = species), color = "magenta") +
  facet_wrap(~species, ncol= 1)
```

-   Fills of areas or polygons are done using fill function

-   points or lines color changes can be done within aes
